High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 overall.tex
suggested tweak in overall.tex.
  Matteo: please review.

PanDA Brokers' efficiency (Fig.~\ref{fig:backfill-utilization}, red labels)
is defined as the fraction (or percentage) of core-hours utilized by the
PanDA Brokers to Titan’s total backfill availability during the experiment
time window. The brokers reached 18\% average efficiency, with a minimum
7.8\% efficiency on May 2016 and a maximum 30.9\% efficiency on February 2017
(excluding the preliminary results of March). The total backfill availability
was 20.3M in April 2016, and 17.6M in February 2017. This shows that the
measured difference in efficiency did not depend on a comparable difference
in the total backfill availability.

>>>>

PanDA Brokers' efficiency (Fig.~\ref{fig:backfill-utilization}, red labels) is
defined as the fraction (or percentage) of core-hours utilized by the PanDA
Brokers to Titan’s total backfill availability during the experiment time
window. The brokers reached 18\% average efficiency, with a minimum efficiency
of 7.8\% (May 2016) and a maximum efficiency of 30.9\% (Feb. 2017, excluding
the preliminary results of March). The total backfill availability was 20.3M
in April 2016, and 17.6M in February 2017. This suggests that the differences
in efficiency did not depend on a comparable difference in the total backfill
availability. \jhanote{change last sentence to: ... efficiency does not depend on total backfill availability." ??}
\jhanote{shouldn't we be consistent in the months used to quote efficiency and
utilization? April 2016 and Feb 2017 vs May 2016 and Feb 2017??}
